Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
combine intro p
rm sri

Social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems [@Krause_2009;
@Wey_2008; @Croft_2011]. It provides insight into the structure of social
communities, which can influence population
dynamics and evolutionary processes [@Pinter_Wollman_2013; @Kurvers_2014]. 
Despite the widespread use and innovation of traditional social
network analysis [@Webber_2019], it typically considers
sociality in a singular context, drastically simplifying the complexity of
animal social systems [@Finn_2019].

Extending traditional monolayer social networks, multilayer networks explicitly
consider social systems across scale-dependent contexts [@Pilosof_2017].
Multilayer networks are composed of multiple layers, each representing (i)
different classes of individuals, e.g. male or female, (ii) types of behaviours,
e.g. grooming, travelling, or foraging, (iii) spatial areas, e.g. local or
regional, (iv) or temporal windows, e.g. daily or seasonal [@Kivela_2014;
@Porter_2018]. Multilayer networks are relatively novel to studies of animal
behaviour [@Silk_2018; @Finn_2019] and integrating scale within these 
remains an unexplored opportunity to develop novel understanding of
animal social systems.

@@

$$ SRI = \frac{x}{x + y_{AB} + y_{A} + y_{B}} $$

where x is the number of fixes where individuals A and B were in the same group,
$y_{A}$ is the number of fixes from individual A when individual B did not have
a simultaneous fix, $y_{B}$ is the number of fixes from individual B when
individual A did not have a simultaneous fix, and $y_{AB}$ is the number of
simultaneous fixes from individuals A and B that were separated by more than the
social distance threshold [@Farine_2015].

>>>>

Social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems [@Krause_2009;
@Wey_2008; @Croft_2011]. It provides insight into the structure of social
communities, which can influence population dynamics and evolutionary processes
[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use and innovation
of traditional social network analysis [@Webber_2019], it typically considers
sociality in a singular context, drastically simplifying the complexity of
animal social systems [@Finn_2019]. Extending traditional monolayer social
networks, multilayer networks explicitly consider social systems across
scale-dependent contexts [@Pilosof_2017]. Multilayer networks are composed of
multiple layers, each representing (i) different classes of individuals, e.g.
male or female, (ii) types of behaviours, e.g. grooming, travelling, or
foraging, (iii) spatial areas, e.g. local or regional, (iv) or temporal windows,
e.g. daily or seasonal [@Kivela_2014; @Porter_2018]. Multilayer networks are 
relatively novel to studies of animal behaviour [@Silk_2018; @Finn_2019] and 
integrating scale within these remains an unexplored opportunity to develop 
novel understanding of animal social systems.

@@
